---
params:
  subtitle: "Something"
  c: "x"
  dir_file: "abc"
  
title: 'Individual report for'
subtitle: '`r params$subtitle`'
date: "`r Sys.Date()`"
format:
  pdf:
    classoption: portrait, a4paper
    papersize: A4
    include-in-header:
      text: |
        \addtokomafont{disposition}{\rmfamily}
editor: visual
fontsize: 10pt
number-sections: TRUE
---

```{r setup, include=FALSE, echo = FALSE}
      knitr::opts_chunk$set(echo = TRUE, dev="cairo_pdf")
      source(params$dir_file)
      select.individual(params$c)
```

# Individual description

Name: `r params$subtitle`

Species: `r as.character(unlist(ind_data[,1]))`

Sex: `r as.character(unlist(ind_data[,7]))`

Place of residence: `r as.character(unlist(ind_data[,2]))`

# Bill length

My bill length: `r format(as.numeric(ind_data[,3]), nsmall = 2)` mm

```{r, echo=FALSE, fig.align='right',warnings = FALSE, fig.height=2.5}
    plot.graph(1)
```

\newpage

# Bill depth

My bill depth: `r format(as.numeric(ind_data[,4]), nsmall = 2)` mm

```{r, echo=FALSE, fig.align='right',warnings = FALSE, fig.height=2.5}
    plot.graph(2)
```

# Flipper lenght

My flipper length: `r format(as.numeric(ind_data[,5]), nsmall = 0)` mm

```{r, echo=FALSE, fig.align='right',warnings = FALSE, fig.height=2.5}
    plot.graph(3)
```

\newpage

# Weight

My weight: `r format(as.numeric(ind_data[,6]), nsmall = 0)` g

```{r, echo=FALSE, fig.align='right',warnings = FALSE, fig.height=2.5}
    plot.graph(4)
```
